---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CTVsuggest

<!-- badges: start -->
<!-- badges: end -->

The aim of CTVsuggest is to provide recommendations for packages to be added to available [CRAN Task Views](https://github.com/cran-task-views/ctv#available-task-views).  

The CTVsuggest R package has a single simple function: `CTVsuggest()`, that outputs package suggestions.  

The model training is carried out by the [CTVsuggestTrain](https://dylandijk.github.io/CTVsuggestTrain/) package, for further detail on the workflow view the [Packages Workflow Section](https://dylandijk.github.io/CTVsuggest/articles/CTVsuggest-Overview.html#the-package-workflow) of the [CTVsuggest Overview Vignette](https://dylandijk.github.io/CTVsuggest/articles/CTVsuggest-Overview.html).


## Installation

You can install the development version of CTVsuggest from GitHub with:

``` r
# install.packages("devtools")
devtools::install_github("DylanDijk/CTVsuggest")
```

## Example

`CTVsuggest()` function takes a Task View name (`taskview`) and `n` as arguments. Then outputs a `data.frame` containing the top `n` recommendations for the chosen Task View.

```{r example}
library(CTVsuggest)

CTVsuggest(taskview = "NaturalLanguageProcessing", n = 5)
```


