---
title: "CTVsuggest Overview"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{CTVsuggest Overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Objective of the CTVsuggest Package

The [CRAN Task Views](https://github.com/cran-task-views/ctv#available-task-views) are maintained by volunteers and are always welcome to contributions for
additional content from members of the community. Due to the huge number of packages
that are in CRAN it is infeasible for a Task View maintainer to review all of the available
packages. Therefore, a [model](#the-model) that would give suggestions for the maintainer to then review would be useful.

The aim of CTVsuggest is to give suggestions for packages to be added to [CRAN Task Views](https://github.com/cran-task-views/ctv#available-task-views). There is a single function, `CTVsuggest()`, that outputs these suggestions.

<!-- - The prediction probabilities are computed using [`CTVsuggestTrain::Train_model()`](https://dylandijk.github.io/CTVsuggestTrain/reference/Train_model.html) -->

## CTVsuggest Example

<!-- I have given the package and function the same name so that it is easy to remember, both are named **CTVsuggest**. -->

First install the CTVsuggest package:
```{r, warning = FALSE, message = FALSE, results='hide', eval=FALSE}
library(devtools)
install_github("DylanDijk/CTVsuggest")
```

Then attach the package.
```{r}
library(CTVsuggest)
```


To output the top 5 suggested packages for the [NaturalLanguageProcessing Task View](https://github.com/cran-task-views/NaturalLanguageProcessing/).

```{r}
CTVsuggest(n = 5, taskview = "NaturalLanguageProcessing")
```


## The Package Workflow
Alongside the CTVsuggest package there is the [CTVsuggestTrain](https://dylandijk.github.io/CTVsuggestTrain/) package.  

CTVsuggestTrain contains functions which execute the training of the model. In particular, [`CTVsuggestTrain::Train_model()`](https://dylandijk.github.io/CTVsuggestTrain/reference/Train_model.html) trains a multinomial logistic regression model, where the outcome categories are the available CRAN Task Views plus an additional `"none"` category. In addition, after training the model, `Train_model()` returns a `data.frame` containing the predicted classification probabilities of CRAN packages to CRAN Task Views.

The current workflow is that I run the [`CTVsuggestTrain::Train_model()`](https://dylandijk.github.io/CTVsuggestTrain/reference/Train_model.html) function weekly, each time storing the `data.frame` of predicted probabilities on the [CTVsuggestTrain GitHub repo](https://github.com/DylanDijk/CTVsuggestTrain). The CTVsuggest package then loads this `data.frame` to output suggestions for different Task Views as shown in the [example](#ctvsuggest-example).



## The Model

I now provide a high level view of how the model is trained. The [CTVsuggestTrain Section](#ctvsuggesttrain) then provides an overview of the CTVsuggestTrain package which executes the model training, the section also contains links to the functions documentation and source code.


### Multinomial Logistic Regression
The model aims to give a Task View suggestion after being giving a set of features of an unassigned CRAN R package. There exist packages that are assigned to multiple Task Views, but I have looked at classifying packages to a single Task View. Therefore, I have set this up as a multi-class classification problem, compared to a multi-label problem. 

However, it would not be reasonable to assign a Task View to every package. This would depart from the objective of Task Views^[[CRAN Task View Initiative](https://github.com/cran-task-views/ctv#cran-task-view-initiative-)], which is to give a sharp focus on packages that are needed for a task. For this reason, the model also has the possibility of assigning a package to no Task View. Therefore, I have included an additional `"none"` outcome category and hence the number of possible labels in this classification problem is the number of Task Views + 1.

To perform this multi-class classification problem I have used a Multinomial Logistic model with a LASSO penalty, trained using the `glmnet::cv.glmnet()` function. The `cv.glmnet()` function performs cross-validation over a grid of lambda values, providing a measure of performance for each of the lambda values. I then select the model which has the lowest average multinomial deviance across the folds (`lambda.min`).

### Features

In order to construct the Multinomial Logistic model, I need to create a set of features for the CRAN packages.

I have used three different types of data to create the features for this model:  
(I let $n$ denote the number of currently available Task Views)

- [Text data from Package and Task View descriptions](#text-data-from-package-and-task-view-descriptions). $n$ features
- [Package dependencies](#package-dependencies). $n + 1$ features
- [Other Packages developed by the Authors](#authors-other-packages). $n + 1$ features

I will now go into more detail into how I constructed features from this data.

#### Text data from Package and Task View descriptions


- Each Task View has a page with text describing its scope
  - Example: [Econometrics Task View description](https://cran.r-project.org/web/views/Econometrics.html)
- Each package on CRAN has a title and description describing the purpose of the package 
  - Example: [fxregime package web page](https://cran.r-project.org/web/packages/fxregime/index.html)


I extract the Task View text data from their corresponding markdown files, which are stored in the GitHub repository of the corresponding Task View.
I also extract the titles and descriptions for each of the packages. I then measure the similarity between the package text to each Task View text to create $n$ features.

<!-- For example the [Econometrics Task View Markdown file](https://github.com/cran-task-views/Econometrics/blob/main/Econometrics.md)   is stored in the  Econometrics GitHub repositor. All of the GitHub repositories can be found in the  [cran-task-views](https://github.com/cran-task-views) GitHub account. -->

#### Package Dependencies

For each package, I look at the immediate hard dependencies to other packages, and then calculate the proportion of the assignment of these packages to Task Views.

#### Authors Other Packages

For each package I look at all of the other packages created by the authors of that package. I then calculate the proportion of these packages that are assigned to each Task View.    


### Training Data

To train and test the model I used packages that were assigned a Task View, I also used a set of packages which I labelled as not belonging to a Task View.
The large proportion of packages not belonging to a Task View would have not been reviewed by Task View maintainers, and so would not be
representative for packages belonging to the `“none”` category.Therefore to choose the packages to include that are labelled as belonging to the `“none”`
category, we select packages that have a high amount of monthly downloads

Then from this set of packages I split it with an 80:20 ratio, into a training and testing set.

### Predictions

Using the trained model, I can get predictions by looking at the predicted classification probabilities when given the set of features of a package.
I output the predicted classification probabilities for the packages that are not assigned a Task View and do not meet the monthly download threshold I mentioned in the previous section.

### Accuracy

The accuracy of the model can then be measured by comparing the trained model predictions with the testing set.

In particular, I set the predicted Task View to be the one with the largest predicted probability. The accuracy is then measured as the
proportion of correct predictions on the testing set. For packages that are assigned to multiple Task View, I set a prediction as accurate if its
prediction is one of its assigned Task Views.



## CTVsuggestTrain

First install the **CTVsuggestTrain** package:
```{r, warning = FALSE, message = FALSE, results='hide'}
library(devtools)
install_github("DylanDijk/CTVsuggestTrain")
```

As mentioned above, the training of the models is performed with the `CTVsuggestTrain::Train_model()` function. This function uses four internal functions of the CTVsuggestTrain package which are run in order: 

- `get_data()`
- `get_NLP()`
<!-- Using all of the text from the Task View I have created a corpus. Then for each word I calculated the term frequency -->
<!-- For each package I have combined the title and description text, then I have vectorised this text as well as the Task View text. -->
<!-- Then for each package I have calculated the cosine similarity between its text vector against all of the Task Views text vectors.  -->

- `get_create_features()`
- `get_CRAN_logs()`








<!-- Due to the huge number of packages -->
<!-- that are in CRAN it is infeasible for a Task View maintainer to review all of the available -->
<!-- packages.Therefore, a model that would give a small selection of high quality suggestions -->
<!-- for the maintainer to then review would be useful. Such a model would also be useful from the perspective of a package developer. After -->
<!-- publishing their package onto CRAN, they could then check whether they should propose -->
<!-- their package to one of the Task View maintainers. -->


<!-- The model we want to construct should give a Task View suggestion after being giving -->
<!-- some set of features of an unassigned package. However, it would not be reasonable to -->
<!-- assign a Task View to every package. This would depart from the objective of Task Views, -->
<!-- which is to give a sharp focus on packages that are needed for a task. For this reason, the -->
<!-- model should also have the possibility of assigning a package to no Task View. -->
<!-- Consequently, the model should have a multicategory response variable, made up of 37 categories. The 36 Task Views with an -->
<!-- additional “None” category. -->


